Copulas and their potential for ecology

### 2019-12-17 Paper.Rmd
continued eidtorial to satisfy referee comments

<!--bivariate example, model selection-->
For the soil C and N data (section \ref{Data}, Table \ref{tab_data_info}, 
Fig. \ref{fig_biv_multi_raw_cop}A), variables were 
non-independent ($p=$ `r BivMS_res_Loecke$IndepTestRes`, to within the precision available 
from `BiCopIndTest` in the `VineCopula` package). Non-independence is also visually apparent.
The Kendall correlation was `r round(BivMS_res_Loecke$TauVal,2)`. We fitted our 16 copulas
to the normalized ranks (Fig. \ref{fig_biv_multi_raw_cop}E) 
and computed AIC and BIC weights and corresponding
lower- and upper-tail statistics for the fitted distributions (Table \ref{tab_soilCNfit}).
`r BivMS_res_Loecke$InfCritRes$copname[which.min(BivMS_res_Loecke$InfCritRes$AIC)]` was the 
minimum-AIC copula, with AIC `r round(min(BivMS_res_Loecke$InfCritRes$AIC),2)`, whereas the 
normal copula had a much higher AIC, `r round(BivMS_res_Loecke$InfCritRes$AIC[1],2)`, answering the 
first part of Q1 for these data. Recall that AIC differences of $2$
or $3$ are considered meaningful and differences of $8$ or greater
are considered definitive, so that data provide essentially no support
for the higher-AIC model in that case [@burnham2003_modelselection].
Model-averaged lower- and upper-tail dependence statistics were `r round(BivMS_res_Loecke$relLTdep_AICw,3)` 
and `r round(BivMS_res_Loecke$relUTdep_AICw,3)`, respectively (AIC weights were used for averaging). 
These values are distinct from what a normal copula would give, namely, 0, helping to answer 
the second part 
Q1 for these data. The values also differed substantially 
from each other, helping answer the third part of Q1. 
The numbers reflect stronger upper- than lower-tail
dependence, and this is also visible in the extreme upper-right
and lower-left corners of the copula plot (Fig. \ref{fig_biv_multi_raw_cop}E).

>>>>

<!--bivariate example, model selection-->
For the soil C and N data (section \ref{Data}, Table \ref{tab_data_info}, 
Fig. \ref{fig_biv_multi_raw_cop}A), variables were 
non-independent ($p=$ `r BivMS_res_Loecke$IndepTestRes`, to within the precision available 
from `BiCopIndTest` in the `VineCopula` package). Non-independence is also visually apparent.
The Kendall correlation was `r round(BivMS_res_Loecke$TauVal,2)`. We fitted our 16 copulas
to the normalized ranks (Fig. \ref{fig_biv_multi_raw_cop}E) 
and computed AIC and BIC weights and corresponding
lower- and upper-tail statistics for the fitted distributions (Table \ref{tab_soilCNfit}).
`r BivMS_res_Loecke$InfCritRes$copname[which.min(BivMS_res_Loecke$InfCritRes$AIC)]` was the 
minimum-AIC copula, with AIC `r round(min(BivMS_res_Loecke$InfCritRes$AIC),2)`, whereas the 
normal copula had a much higher AIC, `r round(BivMS_res_Loecke$InfCritRes$AIC[1],2)`, answering the 
first part of Q1 for these data: these data have a dependence structure markedly distinct 
from that of a normal copula. Recall that AIC differences of $2$
or $3$ are considered meaningful and differences of $8$ or greater
are considered definitive, so that data provide essentially no support
for the higher-AIC model in that case [@burnham2003_modelselection].
Model-averaged lower- and upper-tail dependence statistics were `r round(BivMS_res_Loecke$relLTdep_AICw,3)` 
and `r round(BivMS_res_Loecke$relUTdep_AICw,3)`, respectively (AIC weights were used for averaging). 
These values are distinct from what a normal copula would give, namely, 0, helping to answer 
the second part 
Q1 for these data. The values also differed substantially 
from each other, helping answer the third part of Q1. 
The numbers reflect stronger upper- than lower-tail
dependence, and this is also visible in the extreme upper-right
and lower-left corners of the copula plot (Fig. \ref{fig_biv_multi_raw_cop}E).
